\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[francais]{babel}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}

\begin{document}
    \thispagestyle{empty}
    \begin{tabular}{p{10cm}p{10cm}}
        Alain DRILLON & Roger Eastwood \\
        Sales manager at MicroAppoogle, Inc. & Homework manager at Slezak, Inc. \\
        Year 2 Group 1 & Washington, Britannic Empire \\
        Pyongyang, DPRK & \\
    \end{tabular}

    \vspace{3cm}

    Dear Mr. Eastwood,
    \vspace{0.5cm}

    You are one of our most valued customers, that is why we are making you this special offer. Last year, we provided new smartphones for your employees, and they were all really pleased about it. Since you are a wise person, you sure know that in order for your company to be productive and effective, you must offer the best working equipment to your employees, so they can use their full potential at work.

    This is why we offer you and your company to replace these old, obsolete smartphones your employees use, by brand new iGalaxy 4S. We will be very happy to buy back the old phones before selling you the new ones, thus giving you a 85\% discount for the phones.

    Our brand new iGalaxy 4S have awesomely awesome new functionalities to increase your employees' productivity and your company's profits :
    \begin{itemize}
        \item \textbf{Waterproof!} Now your employees won't fear losing their hard work by dropping the phone in a frozen lake or in the toilet!
        \item \textbf{Lavaproof!} Now your employees won't fear losing their hard work by dropping the phone in a volcano or in the toilet!
        \item \textbf{Cloud storage!} Your employees can store their work on a NSA-approved cloud storage service, so they (and the government) can access it anywhere, at any time!
        \item \textbf{American!} Your employees will enjoy more freedom and democracy with these 100\% American phones!
    \end{itemize}

    We at MicroAppoogle offer you this exclusive offer to reward your loyalty to our brand. We hope to hear about you claiming this offer very soon !

    \vspace{0.5cm}
    Sincerely,

    Alain DRILLON
\end{document}
